---
title: "Penguins Vis"
author: Sophia Brown
format: html
---

### Penguins are cool!

Penguins have been peoples fascinations for millennial. I strive to provide visuals of their anatomy, population, and the inner workings of correlation to one another.

This data was introduced and provided to me through the CS 201 Introduction to R class. As I have worked with this data set for almost 8 weeks, I have gotten very familiar with it and had much practice with it regarding Data Vis.

I chose this data due to my own strengths and familiarity with the data itself. I also genuinely find penguins interesting, especially their anatomy and inability to fly.

This is the Penguins' data:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse) 
library(here)
library(palmerpenguins)
library(janitor)
library(plotly)
library(ggiraph)
```

This graph illustrates the relationship between body mass of penguins and their flipper length.

```{r, echo=FALSE, message=FALSE, warning=FALSE}

ggplot(penguins, aes(x = body_mass_g, y = flipper_length_mm, color = species)) +
  geom_point() +
  labs(
    title = "Body Mass vs. Flipper Length",
    x = "Body Mass (g)",
    y = "Flipper Length (mm)"
  ) +
  theme_minimal() +
  theme(legend.position = "none") +
geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(values = c("#3E92CC", "#2A628F", "#13293D"))

```

This second data visualization shows the positive correlation of culmen length and flipper length.

```{r, echo=FALSE, message=FALSE, warning=FALSE}

ggplot(penguins, aes(x = culmen_length_mm, y = flipper_length_mm, color = species)) +
  geom_point(size = 3, alpha = 0.8) +
  labs(
    title = "Flipper Length vs. Culmen Length",
    x = "Culmen Length (mm)",
    y = "Flipper Length (mm)"
  ) +
  theme_minimal() +
  theme(legend.position = "none") +
geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(values = c("#3E92CC", "#2A628F", "#13293D"))
```

This last visualization expresses the strong relationship between the species of penguin and their habitat (island).

```{r, echo=FALSE, message=FALSE, warning=FALSE}

ggplot(penguins, aes(x = island, y = species, color = species)) +
  geom_jitter(size = 3, alpha = 0.8, width = 0.2, height = 0.2) +
  scale_color_manual(values = c("#3E92CC", "#2A628F", "#13293D")) +
  labs(
    title = "Species Distribution Across Islands",
    x = "Island",
    y = "Species"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```
