---
title: "Penguins Vis"
author: Sophia Brown
format: html
---

### Penguins are cool!

Penguins have been peoples fascinations for millennial. I strive to provide visuals of their anatomy, population, and the inner workings of correlation to one another.

This data was introduced and provided to me through the CS 201 Introduction to R class. As I have worked with this data set for almost 8 weeks, I have gotten very familiar with it and had much practice with it regarding Data Vis.

I chose this data due to my own strengths and familiarity with the data itself. I also genuinely find penguins interesting, especially their anatomy and lack of ability to fly.

This is the Penguins' data:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse) 
library(here)
library(palmerpenguins)
library(janitor)
library(plotly)
library(ggiraph)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}

ggplot(penguins, aes(x = body_mass_g, y = flipper_length_mm, color = species)) +
  geom_point() +
  labs(title = "Body Mass vs. Flipper Length") +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  )
```

This data illustrates

```{r, echo=FALSE, message=FALSE, warning=FALSE}

ggplot(penguins, aes(x = culmen_length_mm, y = flipper_length_mm, color = species)) +
  geom_point(size = 3, alpha = 0.8) +
  labs(
    title = "Flipper Length vs. Culmen Length",
    x = "",
    y = ""
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```

This data illustrates

```{r, echo=FALSE, message=FALSE, warning=FALSE}

ggplot(penguins, aes(x = island, y = species, color = species)) +
  geom_jitter(size = 3, alpha = 0.8, width = 0.2, height = 0.2) +
  labs(
    title = "Species by Island", x = "Island", y = "Species", color = "Species") +
  theme_minimal()
```

This data illustrates

```{r}

ggplot(penguins, aes(x = island, y = species, color = species)) +
  geom_jitter(size = 3, alpha = 0.8, width = 0.2, height = 0.2) +
  labs(
    title = "Species Distribution Across Islands",
    x = "",
    y = ""
  ) +
  theme_minimal() +
  theme(legend.position = "none")

```
